Paper_analyses

### 2022-02-09 Paper_Analyses_subj_obje_arousal.Rmd
started reshuffling for null hypothesis testing
one approach to test significance of esimates is to destroy the relational structure in the data e.g. via reshufling of variables (within the respective hierarquies like subject). this creates a null distribution against which we can test our observed estimates

res.mfa <- MFA(clustering_new_pre_PCA_2, 
               group = c(2, 1, 1, 1), 
               type = c("n", "s", "s", "s"),
               name.group = c("pp_stim","pupil","HR","SCR"),
               # num.group.sup = c(1,2),
               graph = TRUE)

@@

TInPosition::
```

@@

library(FactoMineR)
??HMFA

H_n<- clustering_new_pre_PCA3.1.scale%>%
  group_by(ssid)%>%
  mutate(n = n())%>%
  summarise_at(c("n"), mean, na.rm = TRUE)

H_n.1<- H_n$n

as.list(H_n.1)
c(H_n.1)

hierar<- list(c(H_n.1))

View(wine)
FactoMineR::HMFA(clustering_new_pre_PCA3.1.scale[,2:7],
                 H = hierar, 
               # group = c(1, 3, 2), 
               type = c("n", "s", "s",  "s", "s",  "s"),
               # "s", "s", "s"
               name.group = c("pp_stim","auton","subj"),
               # num.group.sup = c(1),
                 # ncp = 
               # ind.sup = c(1,2),
               graph = TRUE)

# okay try and aggregate  response per stimuli

@@

@@

 FactoMineR::MFA(clustering_new_pre_PCA3.1.scale_agg_bysid, 
               group = c(1, 3, 2), 
               type = c("n", "s", "s"),
               # "s", "s", "s"
               name.group = c("stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

>>>>

```{r}
res.mfa <- MFA(clustering_new_pre_PCA_2, 
               group = c(2, 1, 1, 1), 
               type = c("n", "s", "s", "s"),
               name.group = c("pp_stim","pupil","HR","SCR"),
               # num.group.sup = c(1,2),
               graph = TRUE)

@@

# validation
# -	Some idea, get p values for factorminer – dimensions, and correklations
# -	Stability of firt 2 dimensions by resampling

res.mfa_bio_vs_self2_k2<- FactoMineR::MFA(clustering_new_pre_PCA3.1[,1:9], 
               group = c(4, 3, 2), 
               type = c("n", "s", "s"),
              ind.sup = c(1),
              ncp = 2,
               name.group = c("pp_stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

# 
# quanti

# randomly resample withouth replacement

?FactoMineR::simule()

clustering_new_pre_PCA3.1$stimDescription<- as.factor(clustering_new_pre_PCA3.1$stimDescription)

clustering_new_pre_PCA3.1$ssid_stim<- paste0(clustering_new_pre_PCA3.1$ssid,
                                             paste0(clustering_new_pre_PCA3.1$stimDescription))

clustering_new_pre_PCA3.1$ssid_stim<- as.factor(clustering_new_pre_PCA3.1$ssid_stim)

unique(clustering_new_pre_PCA3.1$ssid)

# this will simulkate 61 times (we can assum that 51 paticipants)

testsim$simul

# clustering_new_pre_PCA3.1$stimDescription

val_cutlabels<- clustering_new_pre_PCA3.1%>%
  group_by(stimDescription,val_cut_iaps) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  select(c("stimDescription", "val_cut_iaps"))

testsim<- FactoMineR::simule(clustering_new_pre_PCA3.1[,c(2,5:9)], 1)
# then fit pca store the
testsim_withlabels <- left_join(testsim$simul, val_cutlabels)
View(testsim_withlabels)
# then do it again a 100 times

# correlation between variable and dimension

res.mfa_bio_vs_self2_k2[["quanti.var"]][["coord"]]

res.mfa_bio_vs_self2_k2$eig[1:2,]

# https://declaredesign.org/r/fabricatr/reference/resample_data.html

resample_data(clustered_survey, N = 5, ID_labels = "clusters")

unique(clustering_new_pre_PCA3.1$ssid)
clustering_new_pre_PCA3.1[,c(1,2,5:9)]

testres<- resample_data(clustering_new_pre_PCA3.1 [,c(1,2,5:9)], N = 51, ID_labels = "ssid")

# resample_data(clustering_new_pre_PCA3.1[,c(1,2,5:9)], N = 51, 
#               ID_labels = c("ssid","stimDescription")) this can throw errior fu to unbalances

# pca
resampled_temp
# create emopty dataframe
resamp_1st<- data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(resamp_1st)<- names(resampled_temp)

# create emoty  storage rame for eigenvakues
eigen_first<- as.data.frame(eugentest)
eigen_first[,]<- NA

# eigen_first<- as.data.frame(eigen_first)

# create empty storage for correlations
cor_first<- as.data.frame(cortest)
cor_first[,]<- NA
# cor_first<- as.data.frame(cor_first)

# now store group results/partials

res.mfa_bio_vs_self2_k2$group$correlation
partials_first <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
partials_first[,]<- NA
partials_first
partials_first$sim_no<- NA

# i = 1

# for i in 1:100
# set.seed(ran)
# i = 20

unique(resampled_temp_test$ssid)
nrow(resampled_temp_test)

 mean(resampled_temp_test$pup_basCor) #0.6710218

 table(resampled_temp_test$ssid)

 View(resampled_temp_test)

 clustering_new_pre_PCA3.1%>%
   subset(ssid == 1)

resampled_temp_test<- resampled_temp_test %>%
  group_by(ssid, stimDescription, val_cut_iaps)%>%
  mutate(dupe = n()>1)

table(resampled_temp_test$dupe)

 install.packages("fabricatr")
 ??fabricatr::resample_data
 View(resampled_temp_test)
 unique(resampled_temp_test$val_cut_iaps_unique)
 clustering_new_pre_PCA3.1$ssid<- as.character(clustering_new_pre_PCA3.1$ssid)

 table(resampled_temp_test$val_cut_iaps)

 for (i in 1:1000) {
  message(sprintf("$$$$$RUNING sim %i", i))
  resampled_temp_test<- fabricatr::resample_data(clustering_new_pre_PCA3.1 [,c(1,2,3, 5:9)], 
                                  N = c(51,55),
                                  ID_labels = c("ssid", "stimDescription"),
                                  unique_labels = TRUE)
  resampled_temp$sim_no = i

# run PCA on the resampled data
# ?list
    message(sprintf("$$$$$fitting PCA %i", i))
mfa.res_res <- FactoMineR::MFA(resampled_temp[,1:8], 
               group = c(3, 3, 2), 
               type = c("n", "s", "s"),
              # ind.sup = c(1),
              ncp = 2,
               name.group = c("pp_stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = FALSE)

# store the eigen values
  message(sprintf("$$$$$storing PCA %i", i))
eugentest<- as.data.frame(mfa.res_res$eig[1:2,])
eugentest$sim_no<- i

cortest<- as.data.frame(mfa.res_res$quanti.var$cor)
cortest$sim_no = i

partials_temp<- as.data.frame(res.mfa_bio_vs_self2_k2$partial.axes$cor)
partials_temp$sim_no = i
# update the initial d=frames
  message(sprintf("$$$$$upating dataframes %i", i))
  resamp_1st<- (bind_rows(resamp_1st, resampled_temp))
eigen_first<- bind_rows(eigen_first, eugentest)
cor_first<- bind_rows(cor_first, cortest)
partials_first<- bind_rows(partials_first, partials_temp)
  message(sprintf("$$$$$completed iteration%i", i))
}

View(resamp_1st)
View(eigen_first)
View(cor_first)

resamp_1st_N30_withrepl<- resamp_1st
eigen_first_N30_withrepl<- eigen_first
cor_first_N40_withrepl<- cor_first

partials_first_n30_withrepl<- cor_first

# sample a 100?

for (i in 1:1500) {
  message(sprintf("$$$$$RUNING sim %i", i))
  resampled_temp<-  resample_data(clustering_new_pre_PCA3.1 [,c(1,2,3, 5:9)], 
                                  N = 80, ID_labels = "ssid")
  resampled_temp$sim_no = i

# run PCA on the resampled data
# ?list
    message(sprintf("$$$$$fitting PCA %i", i))
mfa.res_res <- FactoMineR::MFA(resampled_temp[,1:8], 
               group = c(3, 3, 2), 
               type = c("n", "s", "s"),
              # ind.sup = c(1),
              ncp = 2,
               name.group = c("pp_stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = FALSE)

# store the eigen values
  message(sprintf("$$$$$storing PCA %i", i))
eugentest<- as.data.frame(mfa.res_res$eig[1:2,])
eugentest$sim_no<- i

cortest<- as.data.frame(mfa.res_res$quanti.var$cor)
cortest$sim_no = i

partials_temp<- as.data.frame(res.mfa_bio_vs_self2_k2$partial.axes$cor)
partials_temp$sim_no = i
# update the initial d=frames
  message(sprintf("$$$$$upating dataframes %i", i))
  resamp_1st<- (bind_rows(resamp_1st, resampled_temp))
eigen_first<- bind_rows(eigen_first, eugentest)
cor_first<- bind_rows(cor_first, cortest)
partials_first<- bind_rows(partials_first, partials_temp)
  message(sprintf("$$$$$completed iteration%i", i))
}

# check if all particiants ocur equally in the old sample
table(resamp_1st_N30_withrepl$ssid)
table(resamp_1st$ssid)

resamp_1st_N80_withrepl<- resamp_1st
eigen_first_N80_withrepl<- eigen_first
cor_first_N80_withrepl<- cor_first

partials_first_n40_withrepl<- partials_first

resamp_1st_N80_withrepl

table(resamp_1st_N30_withrepl$ssid)

##################################################################
# resample hierarquically, use lower n for subject and valence
##################################################################

```{r}
View(resampled_temptest)
colnames(resamp_1st)
colnames(resampled_temp_test)
 # create emopty dataframe
resamp_1st<- data.frame(matrix(NA, nrow = 1, ncol = 13))
# cnames_resamp<- names(resampled_temp)
# colnames(resamp_1st)<- names(resampled_temp)
colnames(resamp_1st)<- cnames_resamp
colnames(resamp_1st)
# create emoty  storage rame for eigenvakues
eigen_first<- as.data.frame(eugentest)
eigen_first[,]<- NA

# eigen_first<- as.data.frame(eigen_first)

# create empty storage for correlations
cor_first<- as.data.frame(cortest)
cor_first[,]<- NA
# cor_first<- as.data.frame(cor_first)

# now store group results/partials

# res.mfa_bio_vs_self2_k2$group$correlation
partials_first <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
partials_first[,]<- NA
partials_first
partials_first$sim_no<- NA

# hierarquical clustering
clustering_new_pre_PCA3.1$ssid<- as.character(clustering_new_pre_PCA3.1$ssid)
clustering_new_pre_PCA3.1$stimDescription<- as.character(clustering_new_pre_PCA3.1$stimDescription)
# having clusters as factors causes a subscript oput of bound error

# think we need to store groups

groups_first<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
# res.mfa_bio_vs_self2_k2$group$correlation

groups_first[,]<- NA
groups_first
groups_first$sim_no<- NA

clustering_new_pre_PCA3.1 [,c(1,2,3, 5:9)]

unique(substr(resampled_temp_test$stimDescription_unique,1,6))
unique(substr(resampled_temp_test$stimDescription_unique,7,30))

#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
for (i in 1:1000) {
  message(sprintf("$$$$$RUNING sim %i", i))
  resampled_temp<- fabricatr::resample_data(clustering_new_pre_PCA3.1 [,c(1,2,3, 5:9)], 
                                  N = c(51,51),
                                  ID_labels = c("ssid", "stimDescription"),
                                  unique_labels = TRUE)
  resampled_temp$sim_no = i
  resampled_temp$ssid_new <- as.factor(substr(resampled_temp$stimDescription_unique,1,6))
  resampled_temp$newstim <- substr(resampled_temp$stimDescription_unique,7,30)
  # resampled_temp$stimDescription<- as.factor(resampled_temp$stimDescription)

# run PCA on the resampled data
# ?list
    message(sprintf("$$$$$fitting PCA %i", i))
    mfa.res_res <- FactoMineR::MFA(resampled_temp[,c(12,2:8)], 
               group = c(3, 3, 2), 
               type = c("n", "s", "s"),
              # ind.sup = c(1),
              ncp = 2,
               name.group = c("pp_stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = FALSE)

# store the eigen values
message(sprintf("$$$$$storing PCA %i", i))
eugentest<- as.data.frame(mfa.res_res$eig[1:2,])
eugentest$sim_no<- i

cortest<- as.data.frame(mfa.res_res$quanti.var$cor)
cortest$sim_no = i

partials_temp<- as.data.frame(mfa.res_res$partial.axes$cor)
partials_temp$sim_no = i

# groups
group_temp<- as.data.frame(mfa.res_res$group$cos2)
group_temp$sim_no = i

# update the initial d=frames
  message(sprintf("$$$$$upating dataframes %i", i))
  resamp_1st<- (bind_rows(resamp_1st, resampled_temp))
eigen_first<- bind_rows(eigen_first, eugentest)
cor_first<- bind_rows(cor_first, cortest)
partials_first<- bind_rows(partials_first, partials_temp)
groups_first<- bind_rows(groups_first, group_temp)
  message(sprintf("$$$$$completed iteration%i", i))
}

resamp_1st
View(resamp_1st)

resamp_1st

resamp_1st_1000boot_hier<- resamp_1st
eigen_first_1000boot_hier<-eigen_first
cor_first_100boot_hier<- cor_first

partials_first_100boot_hier<-partials_first
group_first_100boot_hier<-groups_first

resamp_1st%>%
  subset(sim_no == 11)
resamp_1st%>%
  subset(sim_no == 15)

table(resamp_1st$ssid)
table(resampled_temp_test$ssid)
```
Visualisations

# check component eigenvalues
# quantile(eigenvalue,.05, na.rm = TRUE)
View(eigen_first)

eigen_first$eigenvalue

eigen_first%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
  ggplot(aes(eigenvalue))+
  geom_histogram(alpha = .2)+
    geom_density()+
  # facet_grid(~component)+
    geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
  geom_point(x = res.mfa_bio_vs_self2_k2$eig[1],y = 10,size = 2, color = "red")+

  theme_classic()+
  geom_vline(xintercept = 1, linetype = "dashed")+
  ggtitle("distribution of boostraped eigen values for component  1 
          red dot = observed eigenvalue, boostrapped 95%CI")+
  annotate("text", x = 1.2, y = 20, label = "prob of obs eigen>= boot eigen = 51%")

table(eigen_first$eigenvalue>1)

t.testsample1<- eigen_first%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue) & component == "comp 1" )

t.test(1.14, mu = mean(t.testsample1$eigenvalue))

# boostrap ratio
# proposed by abdi for factir scores
mean(t.testsample1$eigenvalue, na.rm = TRUE)/(sd(t.testsample1$eigenvalue,na.rm = TRUE))

```{r}
# check eigen vectors (correlations

# checpartials_first_n40_withrepl

# check groups

# binom.test(eigen_first$eigenvalue>1)

# calculate the diffeence betwee true eufgenvalye abd boostrap eigenvakue
# and check if it includes zero?

eigen_first%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
  mutate(eigen_d = (mean(eigenvalue))- res.mfa_bio_vs_self2_k2$eig[1])%>%
   mutate(eigen_d2 = eigenvalue- res.mfa_bio_vs_self2_k2$eig[1])%>%

  mutate(perc_5 = quantile(eigen_d2,.025, na.rm = TRUE), 
         perc_95 = quantile(eigen_d2,.975, na.rm = TRUE))%>% #create 95% to descrive interval around the observed estimate
  ggplot(aes(eigen_d2))+
  geom_histogram(alpha = .2)+
    geom_density()+
  # facet_grid(~component)+
    geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
  # geom_point(aes(x = eigen_d,y = 10,size = 2), color = "red")+

  theme_classic()+
    ggtitle("distribution of observed eigenvalue - boot eigenvalues for component  1")+
  annotate("text", x = 0, y = 20, label = "95%CI")

```
  # geom_vline(xintercept = 1, linetype = "dashed")

table(eigen_first$eigenvalue>1)

# boot::boot()

t.test_sample<- eigen_first%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
  mutate(eigen_d = (mean(eigenvalue))- res.mfa_bio_vs_self2_k2$eig[1])%>%
   mutate(eigen_d2 = eigenvalue- res.mfa_bio_vs_self2_k2$eig[1])
t.test(t.test_sample$eigen_d2)

# technially a t test is calculated as the differnce between current mean and pipulation mean devied by population variance, since we often don't have population variance we estimate it from the sample

# will this give us a t?
(res.mfa_bio_vs_self2_k2$eig[1]- (mean(t.test_sample$eigenvalue, na.rm = TRUE)))/ 
  (sd(t.test_sample$eigenvalue))

mean(t.test_sample$eigen_d2)/  (sd(t.test_sample$eigenvalue))

resamp_1st%>%
  subset(sim_no = 1)%>%
  subset(is.na(ssid) == FALSE)%>%
  subset(ssid ==  306)

?fabricatr::fabricate()

library(fabricatr)

# ),
  # pollution = rnorm(N, mean = 5))
fabricatr::fabricate(
  stim = add_level(N = 3),
  id = add_level(N = 30),
  Var1 = runif(N, 2, 10),
  Var2 = runif(N, -5, 6),
  Var2 = runif(N, .2, 2),
  Var4 = runif(N, -10, 10),
  Var5 = runif(N, -10, 10)
))%>%
  arrange(stim)

fabricate(
  primary_schools = add_level(N = 3, 
                              var1 = runif(N, 0, 10)),
  students = link_levels(N = 30,
                          by=join(var1, rho = 0.5)))

# dimension 2

quantile(eigen_first$eigenvalue,.95, na.rm = TRUE)
eigen_first%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>%
    subset(!is.na(eigenvalue) & component == "comp 2" )%>%
  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE),
         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE))%>%
  ggplot(aes(eigenvalue))+
  geom_histogram(alpha = .2)+
    geom_density()+
   geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
  geom_point(x = res.mfa_bio_vs_self2_k2$eig[2],y = 10,size = 2, color = "red")+
  # geom_vline(aes(xintercept = perc_95), linetype = "dotted")+
  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y = 10))+
  theme_classic()

  # first dimension is significant

 # same thing as above with variance
# quantile(eigen_first$`percentage of variance`,.95, na.rm = TRUE)
eigen_first%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>%
  subset(!is.na(`percentage of variance`) & component == "comp 1" )%>%
  mutate(perc_5 = quantile(`percentage of variance`,.025, na.rm = TRUE),
         perc_95 = quantile(`percentage of variance`,.975, na.rm = TRUE))%>%
  ggplot(aes(`percentage of variance`))+
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y = .3), color = "gray30")+
  geom_point(x = res.mfa_bio_vs_self2_k2$eig[1,2],y = .3,size = 3, color = "red")+

    # geom_vline(aes(xintercept = perc_5), linetype = "dotted")+
  # geom_vline(aes(xintercept = perc_95), linetype = "dotted")+
  theme_classic()

```{r}
# let's go to variable correlations with dimenstions

cor_first %>%
  mutate(variable = as.factor(substr(rownames(cor_first), 1,6)))%>%
    subset(!is.na(Dim.1)) %>%
  # create interval per variable
  group_by(variable)%>%
   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  # subset(variable == "arousa"|variable == "valenc")%>%
  # select(c("arousal", "valence"))%>%
  ggplot(aes(Dim.1)) +
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
  facet_grid(~variable)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  #  geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  theme_classic()

cor_first %>%
  mutate(variable = as.factor(substr(rownames(cor_first), 1,6)))%>%
    subset(!is.na(Dim.2)) %>%
  # create interval per variable
  group_by(variable)%>%
   mutate(perc_5 = quantile(Dim.2,.025, na.rm = TRUE),
         perc_95 = quantile(Dim.2,.975, na.rm = TRUE))%>%
  # subset(variable == "arousa"|variable == "valenc")%>%
  # select(c("arousal", "valence"))%>%
  ggplot(aes(Dim.2)) +
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
  facet_grid(~variable)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
   geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  theme_classic()

<!-- partials -->

The graph of partial axes shows the relationship between the principal axes of the MFA and the ones obtained from analyzing each group using either a PCA (for groups of continuous variables) or a MCA (for qualitative variables).
```{r}
View(partials_first)

partials_first%>%
  mutate(dimension = as.factor(substr(rownames(partials_first), 1,4)),
         group = as.factor(substr(rownames(partials_first), 5,9)))%>%
    subset(!is.na(Dim.1)) %>%
  # create interval per variable
  group_by(dimension, group)%>%
   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  ggplot(aes(Dim.1)) +
  geom_histogram(bins = 500)+
  # geom_histogram(aes(y=..density..), alpha=0.5,
  #                position="identity")+
  geom_density(alpha=.2) +
   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =10 ), color = "gray30")+
  facet_grid(dimension~group)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  theme_classic()
  ylim(0,100)

```
graph of groups
```{r}
View(groups_first)
?gather

# we sgoudl probably store cos2 rather than correlatiopn
# their cos2 values corresponding to their quality of representation on the factor map
groups_first%>%
  mutate(group = as.factor(substr(rownames(groups_first), 1,4)))%>%
    subset(!is.na(Dim.1)) %>%
  # create interval per variable

  gather(dimension, value_dimenion, -group, -sim_no) %>%
  # -perc_5,-perc_95, 
   group_by(group,dimension)%>%
   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))%>%

  ggplot(aes(value_dimenion, color = group)) +
  geom_histogram(bins = 500)+
  # geom_histogram(aes(y=..density..), alpha=0.5,
  #                position="identity")+
  geom_density(alpha=.2) +
   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =10 ), color = "gray30")+
  facet_grid(dimension~group)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  theme_classic()
  ylim(0,100)

Do we get the same patterns when loking at paticipants and stimuli searatelly

@@

library(FactoMineR)
??HMFA
```{r}
H_n<- clustering_new_pre_PCA3.1.scale%>%
  group_by(ssid)%>%
  mutate(n = n())%>%
  summarise_at(c("n"), mean, na.rm = TRUE)

@@

########################################

one approach for significance is to create random shuffling that destroys the relational aspect of the data,
e.g. by resshugling the values betwen variabels per participant.
e.g. go to participant one, resgule the order of puopil values for  trials, fo th scr fo the same and so on

clustering_new_pre_PCA3.1_copy<- clustering_new_pre_PCA3.1
colnames(clustering_new_pre_PCA3.1)

?sample

# this is slow so need to figure  a better way to to this but for now
clustering_new_pre_PCA3.1_copy %>%
  subset(ssid == 304 &val_cut_iaps == "mid" & aro_cut_iaps == "low" )%>%
  group_by(ssid)%>%
  transform(pup_basCor = sample(pup_basCor, replace = F),
            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = F),
            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = F),
            arousal = sample(arousal, replace = F),
            valence = sample(valence, replace = F))

colnames(resampled_temp_reshuf)
 # create emopty dataframe
resamp_1st_reshuf<- data.frame(matrix(NA, nrow = 1, ncol = 9))
cnames_resamp_reshufl<- names(resampled_temp_reshuf)

colnames(resamp_1st_reshuf)<- cnames_resamp_reshufl
colnames(resamp_1st_reshuf)
# create emoty  storage rame for eigenvakues
eigen_first_reshuf<- as.data.frame(eugentest)
eigen_first_reshuf[,]<- NA

# eigen_first_reshuf<- as.data.frame(eigen_first_reshuf)

# create empty storage for correlations
cor_first_reshuf<- as.data.frame(cortest)
cor_first_reshuf[,]<- NA
# cor_first_reshuf<- as.data.frame(cor_first_reshuf)

# now store group results/partials

# res.mfa_bio_vs_self2_k2$group$correlation
partials_first_reshuf <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
partials_first_reshuf[,]<- NA
partials_first_reshuf
partials_first_reshuf$sim_no<- NA

# hierarquical clustering
clustering_new_pre_PCA3.1$ssid<- as.character(clustering_new_pre_PCA3.1$ssid)
clustering_new_pre_PCA3.1$stimDescription<- as.character(clustering_new_pre_PCA3.1$stimDescription)
# having clusters as factors causes a subscript oput of bound error

# think we need to store groups

groups_first_reshuf<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
# res.mfa_bio_vs_self2_k2$group$correlation

groups_first_reshuf[,]<- NA
groups_first_reshuf
groups_first_reshuf$sim_no<- NA

#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)

for (i in 1:1000) {
  message(sprintf("$$$$$RUNING sim %i", i))

resampled_temp_reshuf<-    clustering_new_pre_PCA3.1_copy[,c(1,2,3, 5:9)] %>%
  group_by(ssid)%>%
  transform(pup_basCor = 
              sample(pup_basCor, replace = F),
            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = F),
            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = F),
            arousal = sample(arousal, replace = F),
            valence = sample(valence, replace = F))

  resampled_temp_reshuf$sim_no = i
  # resampled_temp_reshuf$ssid_new <- as.factor(substr(resampled_temp_reshuf$stimDescription_unique,1,6))
  # resampled_temp_reshuf$newstim <- substr(resampled_temp_reshuf$stimDescription_unique,7,30)
  # resampled_temp_reshuf$stimDescription<- as.factor(resampled_temp_reshuf$stimDescription)

# run PCA on the resampled data
# ?list
    message(sprintf("$$$$$fitting PCA %i", i))
    mfa.res_reshuf <- FactoMineR::MFA(resampled_temp_reshuf[,c(1:8)], 
               group = c(3, 3, 2), 
               type = c("n", "s", "s"),
              # ind.sup = c(1),
              ncp = 2,
               name.group = c("pp_stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = FALSE)

# store the eigen values
message(sprintf("$$$$$storing PCA %i", i))
eugentest_reshufl<- as.data.frame(mfa.res_reshuf$eig[1:2,])
eugentest_reshufl$sim_no<- i

cortest_reshufl<- as.data.frame(mfa.res_reshuf$quanti.var$cor)
cortest_reshufl$sim_no = i

partials_temp_reshuf<- as.data.frame(mfa.res_reshuf$partial.axes$cor)
partials_temp_reshuf$sim_no = i

# groups
group_temp_reshuf<- as.data.frame(mfa.res_reshuf$group$cos2)
group_temp_reshuf$sim_no = i

# update the initial d=frames
  message(sprintf("$$$$$upating dataframes %i", i))
  resamp_1st_reshuf<- (bind_rows(resamp_1st_reshuf, resampled_temp_reshuf))
eigen_first_reshuf<- bind_rows(eigen_first_reshuf, eugentest_reshufl)
cor_first_reshuf<- bind_rows(cor_first_reshuf, cortest_reshufl)
partials_first_reshuf<- bind_rows(partials_first_reshuf, partials_temp_reshuf)
groups_first_reshuf<- bind_rows(groups_first_reshuf, group_temp_reshuf)
  message(sprintf("$$$$$completed iteration%i", i))
}

@@

res.mfa_agg_bysubj <- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale_agg_bysid, 
               group = c(1, 3, 2), 
               type = c("n", "s", "s"),
               # "s", "s", "s"
               name.group = c("sid","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

boostrap subjct results

factoextra::fviz_eig(res.mfa_agg_bysubj)
factoextra::fviz_mfa_group(res.mfa_agg_bysubj)

res.mfa_bio_vs_self2_k2$eig
res.mfa_agg_bysubj$eig
res.mfa_agg_bysubj$quanti.var$cor
res.mfa_agg_bysubj$group$cos2

```{r}
colnames(resampled_temp_bysubj)
resamp_1st_bysubj<- data.frame(matrix(NA, nrow = 1, ncol = 8))

# cnames_resamp_subj<- names(resampled_temp_bysubj)
colnames(resamp_1st_bysubj)<- cnames_resamp_subj
colnames(resamp_1st_bysubj)
# create emoty  storage rame for eigenvakues
eigen_first_bysubj<- as.data.frame(eugentest)
eigen_first_bysubj[,]<- NA

# eigen_first<- as.data.frame(eigen_first)

# create empty storage for correlations
cor_first_bysubj<- as.data.frame(cortest)
cor_first_bysubj[,]<- NA
# cor_first<- as.data.frame(cor_first)

# now store group results/partials

# res.mfa_bio_vs_self2_k2$group$correlation
partials_first_bysubj <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
partials_first_bysubj[,]<- NA
partials_first_bysubj
partials_first_bysubj$sim_no<- NA

# hierarquical clustering
clustering_new_pre_PCA3.1.scale_agg_bysid$ssid<- as.character(clustering_new_pre_PCA3.1.scale_agg_bysid$ssid)
# clustering_new_pre_PCA3.1.scale_agg_bysid$stimDescription<- as.character(clustering_new_pre_PCA3.1.scale_agg_bysid$stimDescription)

# think we need to store groups

groups_first_bysubj<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
# res.mfa_bio_vs_self2_k2$group$correlation

groups_first_bysubj[,]<- NA
groups_first_bysubj
groups_first_bysubj$sim_no<- NA

#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
colnames(clustering_new_pre_PCA3.1.scale_agg_bysid)

for (i in 1:1000) {
  message(sprintf("$$$$$RUNING sim %i", i))

  resampled_temp_bysubj<- fabricatr::resample_data(clustering_new_pre_PCA3.1.scale_agg_bysid, 
                                  N = c(51),
                                  ID_labels = c("ssid"),
                                  unique_labels = TRUE)
  # View(resampled_temp_bysubj)
  resampled_temp_bysubj$sim_no = i
  # resampled_temp_bysubj$ssid_new <- as.factor(substr(resampled_temp_bysubj$stimDescription_unique,1,6))
  # resampled_temp_bysubj$newstim <- substr(resampled_temp_bysubj$stimDescription_unique,7,30)
  # resampled_temp_bysubj$stimDescription<- as.factor(resampled_temp_bysubj$stimDescription)

# run PCA on the resampled data
  # colnames(resampled_temp_bysubj)
    message(sprintf("$$$$$fitting PCA %i", i))
    mfa.res_bysubj <- FactoMineR::MFA(resampled_temp_bysubj[,1:6], 
               group = c(1, 3, 2), 
               type = c("n", "s", "s"),
              # ind.sup = c(1),
              ncp = 2,
               name.group = c("sid","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = FALSE)
